### 2019-09-16 2019_neurips_vigil/experiments.tex
experiments

\begin{table}[!t]
	\centering
	\caption{COG Dataset parameters for the canonical setting and the hard setting  }
	\resizebox{\textwidth}{!}{

	\begin{tabular}{ccccccc}
		\toprule

		Dataset    &  	number of frames  &  	maximum memory duration & number of distractors & size of training set & size of validation/test set    \\ 
          \midrule

		 Canonical setting & 4 & 3 & 1 & 10000320 & 500016 &   \\
		 \midrule

		 Hard  setting & 8 & 7& 10 & 10000320 & 500016  \\
		 \bottomrule

	\end{tabular}
}

@@

\subsection{Training and testing Methodology}

@@

A more granular analysis of accuracy per task shows a major improvement for the two hardest tasks, AndCompareShape and AndCompareColor. Those two tasks represent a higher level of difficulty due to the number of objects to be remembered in order to answer the question correctly.
As we can see in Table 2 we could achieve a 12\% improvement for the canonical data set and almost a 40\% improvement for the hard dataset.
The large improvement in these memory-intensive tasks indicate that the SAMNet's external memory plays a crucial role in our results. 
The training and implementation details are in appendix.

\begin{table}[t]

@@

	\centering
	\resizebox{\textwidth}{!}{
	\begin{tabular}{ccccccccccc}
		\toprule
		Model & & SAMNet & && && COG&& \\
		\cmidrule{2-5} \cmidrule{7-11} 
		&&&&& & paper & ours & ours & paper&\\
		\cmidrule{7-9} \cmidrule{10-11}
		Trained on       & canonical & canonical & canonical & hard &           &  canonical  & canonical  & canonical & hard \\ 
		Fine tuned on  & - & - & hard  & - &           & -   & - & hard & - \\ 
		Tested on        & canonical & hard & hard & hard &            &canonical  & hard & hard & hard  \\ 
		\midrule

		Overall accuracy & 98.0 & 91.6 & 96.5  &  &           & 97.6  & 65.9 & & 80.1 \\

@@

		AndCompareColor	&	93.5		&	82.7	&	89.2	&&		&81.9	&57.1&  &	51.4
\\ 
		AndCompareShape	&	93.2 		&	83.7	&	89.7	&&	&	80.0	&53.1	& &50.7\\

		\bottomrule
	\end{tabular}
}
	\label{results}
\end{table}

\begin{figure}
	\centering
	\caption{Comparison of SAMNet and COG on their abilities to generalize from the canonical to the hard dataset. We show three different settings: 1) (baseline) trained on canonical, tested on canonical 2) trained on canonical, tested on hard, 3) trained on canonical, fine tuned on hard, tested on hard. }
	\resizebox{6cm}{3.5cm}{%

@@

	\begin{axis}[
	ybar,
	enlargelimits=0.15,
	legend style={at={(0.5,-0.15)},
		anchor=north,legend columns=-1},
	ylabel={COG test accuracy in \% },
	symbolic x coords={canonical/na/canonical, canonical/na/hard, canonical/hard/hard},
	xtick=data,
	nodes near coords,
	nodes near coords align={vertical},
	]
	\addplot coordinates {(canonical/na/canonical,98) (canonical/na/hard,91.6) (canonical/hard/hard,96.5)};
	\addplot coordinates {(canonical/na/canonical,96.7) (canonical/na/hard,65.9) (canonical/hard/hard,70)};
	\legend{SAMNet ,COG Model}
	\end{axis}
	\end{tikzpicture}
}
\end{figure}

>>>>

\begin{table}[!t]
	\centering
	\caption{COG Dataset parameters for the canonical setting and the hard setting  }
	\begin{tabular}{ccc}
		\toprule
		Dataset       &    Canonical setting   & Hard setting   \\

		number of frames      &    4  &  8      \\

		maximum memory duration      &    3   & 7      \\

		number of distractors     &    1   & 10    \\

		size of training set    &    10000320  & 10000320      \\

		size of validation/test set    &    500016   & 500016      \\

		tasks per family  training set   &    227280  & 227280    \\

		tasks per family  validation/test set   &    11364   & 11364      \\

	   \bottomrule

	\end{tabular}

@@

\subsection{Training and Implementation Details}

SAMNet is implmented on IBM's Mi-Prometheus~\cite{kornuta2018accelerating} framework based on Pytorch. 
We trained all our models using NVIDIA’s GeForce GTX TITAN X GPUs. SAMNet was trained using 8 reasoning steps and a hidden state size of 128. The external memory has 128-bit slots for all experiments. We trained our model until convergence but we also have set a training time limit of 80 hours.

@@

A more granular analysis of accuracy per task shows a major improvement for the two hardest tasks, AndCompareShape and AndCompareColor. Those two tasks represent a higher level of difficulty due to the number of objects to be remembered in order to answer the question correctly.
As we can see in Table 2 we could achieve a 12\% improvement for the canonical data set and almost a 40\% improvement for the hard dataset.
The large improvement in these memory-intensive tasks indicate that the SAMNet's external memory plays a crucial role in our results.

\begin{table}[t]
	\tiny

@@

	\centering
	\begin{tabular}{ccccccccccc}
		\toprule
		Model & & SAMNet & && && COG&& \\
		\cmidrule{2-5} \cmidrule{7-11} 
		&&&&& & paper & ours & ours & paper&\\
		\cmidrule{7-9} \cmidrule{10-11}
		Trained on       & canonical & canonical & canonical & hard &           &  canonical  & canonical  & canonical & hard \\ 
		Fine tuned on  & - & - & hard  & - &           & -   & - & hard & - \\ 
		Tested on        & canonical & hard & hard & hard &            &canonical  & hard & hard & hard  \\ 
		\midrule

		Overall accuracy & 98.0 & 91.6 & 96.5  & running &           & 97.6  & 65.9 & running& 80.1 \\

@@

		AndCompareColor	&	93.5		&	82.7	&	89.2	&&		&81.9	&53.1&&	51.4
\\ 
		AndCompareShape	&	93.2 		&	83.7	&	89.7	&&	&	80.0	&57.1	&&50.7\\

		\bottomrule
	\end{tabular}
	\label{results}
\end{table}

\begin{figure}
	\centering
	\caption{Comparison of SAMNet and COG on their abilities to generalize from the canonical to the hard dataset. We show three different settings: 1) (baseline) trained on canonical, tested on canonical 2) trained on canonical, tested on hard, 3) trained on canonical, fine tuned on hard, tested on hard. }

@@

	\begin{axis}[
	ybar,
	enlargelimits=0.15,
	legend style={at={(0.5,-0.15)},
		anchor=north,legend columns=-1},
	ylabel={COG test accuracy in \% },
	symbolic x coords={canonical/na/canonical, canonical/na/hard, canonical/hard/hard},
	xtick=data,
	nodes near coords,
	nodes near coords align={vertical},
	]
	\addplot coordinates {(canonical/na/canonical,98) (canonical/na/hard,91.6) (canonical/hard/hard,96.5)};
	\addplot coordinates {(canonical/na/canonical,96.7) (canonical/na/hard,65.9) (canonical/hard/hard,70)};
	\legend{SAMNet ,COG Model}
	\end{axis}
	\end{tikzpicture}
\end{figure}
